%!TEX TS-program = xelatex
\documentclass[]{kartikkumar-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{KARTIKKUMAR}{ RAO}
       {Senior Software Development Engineer}
          
% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    +91 - 9036560741
    ~
    \href{mailto:kartik.rao24@gmail.com}{kartik.rao24@gmail.com}
    \href{https://github.com/raokartikkumar24}{GitHub}
    \href{https://in.linkedin.com/in/raokartikkumar}{LinkedIn}
    ~
  \section{Skills}
  \section{Programming}
   •C++, C\texttt{\#}
   Basic Knowledge on:
   •Python,Javscript,Lua
    ~
    \section{Tools}
    •Visual Studio
    •Eclipse, Windbg
    \section{Misc}
   •Data structures and Algorithm
   •OS: Windows, Linux
   •Design Patterns, Multi-threading
   ~
   \section{Personal Info}
   •DOB : 24 Oct 1988
   •Passport : K1713302
   ~
\end{aside}

\section{Experience}

\begin{entrylist}
	\entry
	{April-2018}
	{Virsec Systems, Bangalore}
	{Full time}
	{\emph{Software Engineer VSP-Platforms}}
  \entry
    {Jul-2014}
    {McAfee, Bangalore}
    {Full time}
    {\emph{Senior Software Development Engineer in Anti-Malware core}}
  \entry
    {Mar-2013}
    {Oracle India Pvt. Ltd., Bangalore}
    {Ful time}
    {\emph{Software Engineer in Siebel Server core.}}
  \entry
    {Aug-2010}
    {Honeywell Technology Solutions Lab, Bangalore}
    {Full time}
    {\emph{Engineer in HMI Web technology}}
   \entry
   {Jan-2010}
   {Honeywell Technology Solutions Lab, Bangalore}
   {Intern}
   {\emph{Project Trainee in FMS} }
\end{entrylist}

\section{Projects}

\begin{entrylist}
	 \entry
	{2015-2018}
	{Endpoint Security for Mac}
	{C++, Multi-threading}
	{Worked on development of Aribitary Access Control module which involved working
	on kernel and user mode.
	Involved in enhancement and resolving customer issues}
  \entry
    {2014-2015}
    {Anti Malware Core}
    {C++, Python, Multi-threading}
    {Involved in the develpment, enhancement and resolving defects of Anti
    Malware Core product which is the part of McAfee's Anti-Virus Solution.}
  \entry
    {2013-2014}
    {Siebel Server Core}
    {C++, Multi-threading, Data structures and algorithms }
    {Worked on the Siebel Server Core infrastrucre which isa cross-platform
    component of the Siebel CRM application. The server core is a multihreaded
    C++ component that makes the Siebel CRM robust and scable.}
  \entry
    {2010-2013}
    {HMI Web}
    {C++, C\#, asp.net, MFC, VC++}
    {Worked on the Human Machine Interface(HMI) Display builder and station
    which are COM exes and provide high performance vector graphics.Involved in improving the product quality by resolving defects in the product.Involved in the implementation of functionalities using Test Driven
    Development.}
    
  \entry
  {2010-2010}
  {Flight Management System}
  {C\#.net, SQL}
  {Developed a Estimation Tool for flight management system for the
  Aerospace domain which estimates the man hours required to complete a
  module using the various software engineering concepts.}
    
\end{entrylist}


\section{Education}

\begin{entrylist}
  \entry
    {2006–2010}
    {B. Tech }
    {Amrita School of Engineering, Bangalore}
    {Information Technology. CGPA : 8.11}
  \entry
    {2006}
    {PCMB}
    {Karnataka Board}
    {Percentage: 83.83}
  \entry
    {2004}
    {X}
    {Maharashtra Board}
    {Percentage: 83.86}
\end{entrylist}



\end{document}
