%!TEX TS-program = xelatex
\documentclass[]{kartikkumar-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{SAHANA}{ RAO}
       {Technical Lead}
          
% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    +91 - 9632284833
    ~
    \href{mailto:sahana27@gmail.com}{sahana27@gmail.com}
    \href{https://github.com/sahanarao}{GitHub}
    \href{https://www.linkedin.com/in/sahana-rao-3445aa46/}{Linkedin}
    ~
  %\section{Skills}
   \section{Programming}
   •Java - J2EE, Spring, 
   Microservice using Spring Boot, 
   Hibernate, Webservices (Soap and Rest)
   Basic Knowledge on:
   •JBoss Fuse, Apache Camel, ActiveMq
   •AWS
    ~
    \section{Tools}    
    •Eclipse, Intellij, SOAP UI, Postman,
    Maven, Jenkins  
    \section{Servers}
     Apache Tomcat, Web Logic, IBM Web Sphere 7.0
     \section{Database}
     Oracle 10g, DB2
     \section{Configuration Tools}
     Git, SVN
    \section{Misc}
   •Data structures and Algorithm
   •OS: Windows, Linux
   •Design Patterns
   •Experience in Agile projects as Scrum Master
   ~
   \section{Personal Info}
   •DOB : 27 Sep 85
   ~
\end{aside}

\section{Experience}
\begin{entrylist}
	\entry
	{Sep 2007 - May 2020} 
	{ Wipro Technologies, Bangalore}
	{Full time}
	{\emph{Technical Lead}}
	
	\entry
	{Sep 2020 - Present}
	{Datarynx, Bangalore}
	{Full time}
	{\emph{Technical Lead}}
  \end{entrylist}

\section{Projects}

\begin{entrylist}
	\entry		
	{Sep 2020 - Present}
	{Neilsen}
	{Java, Spring Boot, Microservices}
	{As lead, I am responsible for migrating the internal portal used by Data scientists which is on Tibco BW to Spring boot application. Day to day activities includes creating POC's, assigning tasks, code review, attending stand up calls with customer as well as team.}
	\entry		
	{Jan 2019 - Sep 2019}
	{Thor (Capital One)}
	{Java, Spring Boot, Microservices, AWS}
	{As lead, I was solely responsible for all the deliverables of the Sprint. This includes mentoring team members, assigning tasks, reviews. Was also involved in performance testing and bug fixes.}
    \entry
    {Dec 2017 - Dec 2019}
    {Visa - Staff Aug}
    {Java, Spring, Maven, Git, Jenkins}
    {As a lead and scrum master, was involved in sprint wise story analysis, organizing daily stand ups, assigning tasks, estimations, reviews, development and bug fixes of stories. }
    \entry
    {Nov 2016 - Nov 2017}
    {Visa Resolve Online}
    {Jboss Fuse, Apache camel, Core Java, Spring 3.0}
    {Lead migrating IBM Message Broker to JBOSS Fuse and Developing VROL and VCR (VISA Dispute management application)}
     \entry
    {Nov 2013 - Oct 2016}
    {Lloyds Bank}
    {Spring 3.2, Hibernate 3.0, Pro/classic enterprise tool}
    {Requirement analysis and preparing mid level platform design documents. Developing applications for IDM and ATM which monitors the device events and reports to the fault management system.}  
    \entry
    {Jun 2012 - Sep 2013}
    {EPC-IVR}
    {Spring 3.2, Hibernate 3.0}
    {As senior developer, was involved in development, enhancement and bug fixes of the modules in MyDish website.} 
    \entry
    {Jan 2009 - May 2012}
    {British Petroleum}
    {Core Java, Jsp, Struts1.2, EJB, Dream Weaver6.1}
    {As developer, was involved in development, testing and bug fixes of all the websites of BP which includes Castrol, Aral, BP etc.}
    \entry
    {Dec 2007 - Dec 2009}
    {Coca-Cola}
    {Jsp, Servlets, Core Java}
    {Supporting SCM tools, developing POC for intranet site of Coca-Cola}
\end{entrylist}

\section{Education}

\begin{entrylist}
\entry
    {2008–2011}
    {MS - Software Engineering }
    {BITS Pilani (Distance Educations via Wipro}
    {CGPA: 8.7}
  \entry
    {2004–2007}
    {BCA }
    {Miranda Institute of Management Studies, Bangalore}
    {Percentage: 84} 
\end{entrylist}
\end{document}
